The Relationship Between Gender Identities and Regrades among Undergraduate Students, 2010-2016

### 2024-02-14 outputs/paper/paper.qmd
clarify estimand

Our paper will reproduce, ‘Ask and You Shall Receive? Gender differences in Regrades in College’ by Li and Zafar. Accordingly, we ascertain that upon a regrade request, males are more likely to receive a favourable grade change. Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings? Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ Structurally, our paper starts with a brief dissection of the original paper’s findings and our own interpretation of the data. Subsequently, we analyze the results garnered from the data with suitable tables, and double stacked bar charts. Finally, to conclude, we will discuss our findings, entailed by an analysis of the data’s loopholes, ethical biases and future research implications.

>>>>

Our paper will reproduce, ‘Ask and You Shall Receive? Gender differences in Regrades in College’ by Li and Zafar. Accordingly, our estimand asserts that upon a regrade request, males are more likely to receive a favourable grade change regardless of the time during the semester, and regardless of the number of classes that they have. Our study attempts to pose and answer these questions, ‘Does gender bias influence regrade requests in college settings? Are there fluctuations in regrade request patterns among male and female students regarding their class number?’ Structurally, our paper starts with a brief dissection of the original paper’s findings and our own interpretation of the data. Subsequently, we analyze the results garnered from the data with suitable tables, and double stacked bar charts. Finally, to conclude, we will discuss our findings, entailed by an analysis of the data’s loopholes, ethical biases and future research implications.
